A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
https://xkcd.com/1015/
Notational consistency
I like it better when you're on top
Tie this together
Muck around and pretend it's progress

?? Heuristics go here, defer justification until \cref{sec:comparison}

@@

@@

\begin{algorithm}
\DontPrintSemicolon
\nl    \For {$l \in L$}{
\nl        \bf{Let} $P^{''} \gets \{ u \in P^{'} \mid u \neq v \wedge A_G[v][u] = l \}$ \;
\nl        \bf{Let} $T^{''} \gets \{ u \in T^{'} \mid u \neq w \wedge A_H[w][u] = l \}$ \;
\nl        \lIf {$P^{''} \neq \emptyset$ \bf{and} $T^{''} \neq \emptyset$}{$future^{'} \gets future^{'} + \langle P^{''} , T^{''} \rangle$}
       }
\caption{Replacement for \linerangeref{NewPWithEdge}{InnerLoopEnd} in directed and labelled cases}
\label{labDirAlg}
\end{algorithm}

@@

\paragraph{Maximum Common \emph{Connected} Subgraph} The common subgraph must
be connected. We consider only undirected graphs.  Modify \McSplit\ by
permitting branching only on a vertex $v$ that has at least one non-zero
element in its bit-string label.  We can represent this information compactly,
and without increasing time complexity at each search node, by storing an extra
bit with each label class.  This bit takes the value $1$ if and only if the vertices in
the class are adjacent to at least one vertex in $M$.

@@

Experiments were performed on a cluster of machines with Dual Xeon E5-2640
v2 CPUs and 64GBytes RAM.

? MENTION PROGRAMMING LANGUAGES, COMPILER FLAGS, MCSa ALGORITHM AND
BITSET IMPLEMENTATION

%Parallel experiments used 32 threads per machine,
%using all 16 physical cores with hyper-threading enabled.
All ??? experiments used a database of
randomly-generated Maximum Common Subgraph instances, which contains graphs of
order ranging from 10 to 100 vertices
\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}.  For
unlabelled instances, we selected 10 per cent of the 41,100 instances with up
to 40 vertices; labels were discarded. For labelled instances, we selected 10
per cent of the full database of 81,400 instances, and used a labelling scheme
in which the number of distinct vertex labels and the number of distinct edge
labels is approximately equal to 33 per cent of the number of vertices in each
graph.

Small scale experiments (not presented here) were performed to identify a
suitable heuristic for label class selection. The heuristic used selects the
label class  with the smallest $\min(|P|,|T|)$ (a surrogate for expected
branching factor). From this class, a vertex is selected from $P$ with maximum
degree if $H$ is sparse and with minimum degree if $H$ is dense.

@@

\paragraph{No vertex or edge labels, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis)
against number of problem instances solved (y-axis).  There are five contours:
the clique encoding \cite{DBLP:conf/cp/McCreeshNPS16}, CP-FC
\cite{DBLP:conf/cp/NdiayeS11}, \McSplit\, AND TWO OTHERS.  WE NEED CITATIONS
FOR THESE AND ALSO NEED TO CLEAN UP THE LABELS ON THE GRAPHS.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2000 of the 4110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3506 instances that
could be solved by at least one of \McSplit, CP-FC and clique in less than than
1000 seconds, there were only 126 instances on which \McSplit\ was not strictly
faster than the other two solvers.

>>>>

?? Reword for here, explain later Small scale experiments (not presented here)
were performed to identify a suitable heuristic for label class selection. The
heuristic used selects the label class  with the smallest $\min(|P|,|T|)$ (a
surrogate for expected branching factor). From this class, a vertex is selected
from $P$ with maximum degree if $H$ is sparse and with minimum degree if $H$ is
dense.

@@

?? This needs a two sentence intro saying that people care about stuff and why.

@@

\begin{algorithm}[t]
\DontPrintSemicolon
\nl    \For {$l \in L$}{
\nl        \bf{Let} $P^{''} \gets \{ u \in P^{'} : u \neq v \wedge A_G[v][u] = l \}$ \;
\nl        \bf{Let} $T^{''} \gets \{ u \in T^{'} : u \neq w \wedge A_H[w][u] = l \}$ \;
\nl        \If {$P^{''} \negmedspace\neq \emptyset$ \bf{and} $T^{''} \negmedspace \neq \emptyset$}{
    \nl $\AlgVar{future^{'}} \gets \AlgVar{future^{'}} + \langle P^{''}\negmedspace, T^{''} \rangle$}
       }
\caption{Replacement for \linerangeref{NewPWithEdge}{InnerLoopEnd} in directed and labelled cases}
\label{labDirAlg}
\end{algorithm}

@@

\paragraph{Maximum Common \emph{Connected} Subgraph} ?? In applications,
something. The common subgraph must be connected. We consider only undirected
graphs.  Modify \McSplit\ by permitting branching only on a vertex $v$ that has
at least one non-zero element in its bit-string label.  We can represent this
information compactly, and without increasing time complexity at each search
node, by storing an extra bit with each label class.  This bit takes the value
$1$ if and only if the vertices in the class are adjacent to at least one
vertex in $M$. ?? Link to branching scheme papers.

@@

Experiments were performed on machines with dual Intel Xeon E5-2640 v2 CPUs and
64GBytes RAM. Our algorithm was implemented in C++ and compiled using g++
5.3.0. For comparison, we used the implementations of ?? cite clique, kdown,
CP.

Our first set of experiments use a database of randomly-generated maximum
common subgraph instances
\citep{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}.  For
unlabelled instances, we selected the first ten instances from each family
whose members have no more than 50 vertices, for a total of 4,100 instances.
For labelled instances, we selected the first ten instances from every family,
for a total of 8,140 instances with up to 100 vertices; like
\citet{DBLP:conf/cp/McCreeshNPS16}, we use the labelling scheme in which the
number of distinct vertex labels and the number of distinct edge labels is
approximately equal to 33 per cent of the number of vertices in each graph.

@@

\paragraph{Unlabelled, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis)
against number of problem instances solved (y-axis).  There are five contours:
the clique encoding \cite{DBLP:conf/cp/McCreeshNPS16}, CP-FC
\cite{DBLP:conf/cp/NdiayeS11}, \McSplit\, AND TWO OTHERS.  WE NEED CITATIONS
FOR THESE AND ALSO NEED TO CLEAN UP THE LABELS ON THE GRAPHS.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2000 of the 4110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3506 instances that
could be solved by at least one of \McSplit, CP-FC and clique in less than than
1000 seconds, there were only 126 instances on which \McSplit\ was not strictly
faster than the other two solvers.
